Incentives are the biggest barriers to widespread data sharing.

### 2021-04-01 new-paper.Rmd
update title

---
title: Barriers to meaningful data sharing
author: Nicholas J Tierney\* (1,2,3) & Karthik Ram\* (4)
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
csl: nature-communications.csl
header-includes: 
  - \setstretch{1.45}
  - \usepackage[utf8]{inputenc}
---

```{=tex}
\begin{singlespace}

Other titles under consideration:

- Meaningful data sharing
- Data sharing practices to realign incentives and enable positive/meaningful culture change\\
- Enabling culture change for meaningful data sharing\\
- Principles of sharing data\\
- Elements of meaningful data sharing\\
- The biggest barrier to widespread data sharing are incentives and infrastructure.\\
- Some practical guidance on improving data reuse.\\

1 = Monash University, Department of Econometrics and Business Statistics, Melbourne, Australia\\
2 = Australian Centre of Excellence for Mathematical and Statistical Frontiers (ACEMS)\\
3 = Telethon Kids Institute, Perth Children's Hospital, Perth, Australia\\
4 = Berkeley Institute for Data Science, University of California, Berkeley, USA\\
* = Both authors contributed equally to the work\\
Correspondence to:\\
Nicholas Tierney (nicholas.tierney@gmail.com) and Karthik Ram (karthik.ram@berkeley.edu)

\end{singlespace}
```
# Abstract {.unnumbered}

>>>>

---
title: Incentives are the biggest barriers to widespread data sharing.
author: Nicholas J Tierney\* (1,2,3) & Karthik Ram\* (4)
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
csl: nature-communications.csl
header-includes: 
  - \setstretch{1.45}
  - \usepackage[utf8]{inputenc}
---

```{=tex}
\begin{singlespace}
1 = Monash University, Department of Econometrics and Business Statistics, Melbourne, Australia\\
2 = Australian Centre of Excellence for Mathematical and Statistical Frontiers (ACEMS)\\
3 = Telethon Kids Institute, Perth Children's Hospital, Perth, Australia\\
4 = Berkeley Institute for Data Science, University of California, Berkeley, USA\\
* = Both authors contributed equally to the work\\
Correspondence to:\\
Nicholas Tierney (nicholas.tierney@gmail.com) and Karthik Ram (karthik.ram@berkeley.edu)

\end{singlespace}
```

<!-- Other titles under consideration: -->
<!-- Barriers to meaningful data sharing -->
<!-- - Meaningful data sharing -->
<!-- - Data sharing practices to realign incentives and enable positive/meaningful culture change\\ -->
<!-- - Enabling culture change for meaningful data sharing\\ -->
<!-- - Principles of sharing data\\ -->
<!-- - Elements of meaningful data sharing\\ -->
<!-- - The biggest barrier to widespread data sharing are incentives and infrastructure.\\ -->
<!-- - Some practical guidance on improving data reuse.\\ -->

# Abstract {.unnumbered}
